---
title: "Homework 1"
author: "Oksana Prosniakova"
output:
  pdf_document: default
  html_notebook: default
---


## Monte Carlo method

We aim to find the area of the figure bounded by these curves:

$y = 2|x| - \pi;\ \ x \in [-\frac{\pi}{2}, \frac{\pi}{2}]$
<br><br>
$y = |sin(2x)|;\ \ x \in [-\frac{\pi}{2}, \frac{\pi}{2}]$


It can be done using Monte Carlo method. 

From the equations (or a picture) we know that $x_{min} = -\frac{\pi}{2}, \ x_{max} = \frac{\pi}{2}, \ y_{min} = -\pi, \ y_{max} = 1$

The algorithm is the following:

1) Generate a dot with random (x, y) coordinates within the $[x_{min}; x_{max}]\times[y_{min}; y_{max}]$ rectangle;

2) Check whether or not these coordinates are within the given figure;

3) Count the number of dots (k) than pass this criteria;

4) Repeat N times

5) Calculate the area of the figure using this formula:

$S = \frac{k}{N}S_0$

where $S_0$ is the area of the $[x_{min}; x_{max}]\times[y_{min}; y_{max}]$ rectangle
 
```{r}
N <- 100000
k <- 0

for (i in 1:N) {
  x <- runif(1, min = -pi/2, max = pi/2)
  y <- runif(1, min = -pi, max = 1)
  if (y >= 2*abs(x) - pi && y <= abs(sin(2*x))){
    k <- k + 1
  }
}

cat('k =', k)
```

```{r}
S_0 <- pi*(1+pi)
S <- k/N*S_0
```
```{r}
cat('Area of the rectangle: S_0 = ', S_0)
```
```{r}
cat('Area of the figure S = ', S)
```


